Verifying Demonstrations

### 2019-07-02 paper/DB-anon-cred.tex
Minor clarifications, typo fixes

\subsection{Reattempting a distance-bounding Schnorr protocol}%
\label{DBSchnorr}

@@

The main difference between this protocol and the Schnorr protocol is that we 
have the prover compute responses for \(k\) different challenges, \(c_1, 
  \dotsc, c_k\).
However, in the authentication step, the verifier chooses only one of those 
challenges.
From the simulator's (and extractor's) perspective, there is no difference 
whether the verifier first chooses \(k\) and then chooses one of those \(k\) 
challenges, or if the verfifier chooses the one challenge directly;
the distribution is the same, \(\frac{k}{n}\times \frac{1}{k} = \frac{1}{n}\).
Therefore the standard proof for Schnorr as a malicious-verifier \ac{ZKPK} 
protocol with soundness error \(2^{-kn}\) still 
holds~\cite[\eg][]{OnSigmaProtocols}.

@@

\begin{theorem}[\acs*{DBMF} resistance]
  Let \(\adv\) be a \((t, \qobs, \qp, \qv)\)-MF adversary, then 
  \(\Adv_{\DBS}^{\text{MF}}(\adv)\) is negligible.
\end{theorem}

>>>>

\subsection{Reattempting a distance-bounding Schnorr protocol}%
\label{DB-Schnorr}

@@

The main difference between this protocol and the Schnorr protocol is that we 
have the prover compute responses for \(k\) different challenges, \(c_1, 
  \dotsc, c_k\).
However, in the authentication step, the verifier chooses only one of those 
challenges.
From the simulator's (and extractor's) perspective, there is no difference 
whether the verifier first chooses \(k\) and then chooses one of those \(k\) 
challenges, or if the verifier chooses the one challenge directly;
the distribution is the same, \(\frac{k}{n}\times \frac{1}{k} = \frac{1}{n}\).
Therefore the standard proof for Schnorr as a malicious-verifier \ac{ZKPK} 
protocol with soundness error \(2^{-kn}\) still 
holds~\cite[\eg][]{OnSigmaProtocols}.
(We note that \(k\), which is also the length of the challenge bit string, must 
be logarithmic in the security parameter, \(\lambda\), for a malicious 
verifier.)

@@

\begin{theorem}[\acs*{DBMF} resistance]
  Let \(\adv\) be a \((t, \qobs, \qp, \qv)\)-MF adversary, then 
  \(\Adv_{\DBS}^{\text{MF}}(\adv) = (q+k)^n (kq)^{-n}\), where \(k, q\) are as 
  in \cref{DB-Schnorr}.
\end{theorem}
